Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-10-01 prop_letter.tex
prop_letter.tex \section{Gleason} Updating...

In other words, if the measurement intervals are too imprecise, the
results we get might contradict to each other, and exclude any possible
state being consistent with the measurement results. Although we will
not dig into the general framework to avoid this problem here~\citep{HOSTunpublished},
we will solve this problem with a concrete family of intervals and
QIVPMs. Consider the following intervals 
\begin{equation}
\begin{aligned}\mathscr{I}_{n}= & \set{\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]\cap\left[0,1\right]}{k=0,\ldots,2n}\\
 & \cup\{\imposs,\necess\}
\end{aligned}
\end{equation}
which are overlapping intervals with length~$1/n$ except for the
intervals with length~$\left(2n\right)^{-1}$ at each end. As shown
in Table~\ref{tab:I_n}, for each interval~$[\ell,r]$, we define
$\textrm{Int}\left([\ell,r]\right)$, the non-overlapping interior
part of $[\ell,r]$.
\begin{table}
\caption{\label{tab:I_n}Intervals in $\mathscr{I}_{n}$, their lengths, and
their interiors, where $2\mid k$ means $k$ is even, and $2\nmid k$
means $k$ is odd. Although intervals~$[\ell,r]$ are overlapping,
their interior~$\textrm{Int}\left([\ell,r]\right)$ are non-overlapping.}

\begin{tabular}{cccc}
\toprule 
\addlinespace
$k$ & $[\ell,r]$ & $r-\ell$ & $\textrm{Int}\left([\ell,r]\right)$\tabularnewline\addlinespace
\midrule
\midrule 
\addlinespace
 & $\imposs$ & $0$ & $\imposs$\tabularnewline\addlinespace
\midrule 
\addlinespace
$0$ & $\left[0,\tfrac{1}{2n}\right]$ & $\tfrac{1}{2n}$ & $\left(0,\tfrac{0.5}{2n}\right]$\tabularnewline\addlinespace
\midrule 
\addlinespace
\begin{tabular}{c}
$0<k<2n$\tabularnewline
and $2\nmid k$\tabularnewline
\end{tabular} & $\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]$ & $\tfrac{1}{n}$ & $\left(\tfrac{k-0.5}{2n},\tfrac{k+0.5}{2n}\right)$\tabularnewline\addlinespace
\midrule 
\addlinespace
\begin{tabular}{c}
$0<k<2n$\tabularnewline
and $2\mid k$\tabularnewline
\end{tabular} & \multirow{1}{*}{$\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]$} & $\tfrac{1}{n}$ & $\left[\tfrac{k-0.5}{2n},\tfrac{k+0.5}{2n}\right]$\tabularnewline\addlinespace
\midrule 
\addlinespace
$2n$ & $\left[\tfrac{2n-1}{2n},1\right]$ & $\tfrac{1}{2n}$ & $\left[\tfrac{2n-0.5}{2n},1\right)$\tabularnewline\addlinespace
\midrule 
\addlinespace
 & $\necess$ & $0$ & $\necess$\tabularnewline\addlinespace
\bottomrule
\end{tabular}
\end{table}
Since their interior parts are non-overlapping, we can define a function~$\iota_{n}:\left[0,1\right]\rightarrow\mathscr{I}_{n}$
by $\iota_{n}\left(x\right)=[\ell,r]$ if $x\in\textrm{Int}\left([\ell,r]\right)$.
After we have the way mapping a real-valued probability to an interval-valued
one, we can induce a QIVPM from a state according to the following
theorem:

@@

In contrast with the QIVPM defined in Thm.~\ref{thm:Non-extensible-of-Gleason's},
there is always a state consistent with a Born QIVPM~$\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$,
because $\rho\in\coreBorn\left(\left[\mu_{\rho}^{\mathrm{B}}\right]_{n},\events\right)$.
Moreover, by introducing a notion of distance between two states~$\rho$
and $\rho'$ as $\left\Vert \rho-\rho'\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho-\rho'}{\psi}\right|$~\citep{544199},
the collection of states consistent with $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$
gets closer and closer to $\rho$ as the intervals get narrower and
narrower.

@@

\noindent Given a state~$\rho'$ consistent with $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$,
we have $\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)\in\iota_{n}\left(\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right)$
on any 1-dimensioal projector~$\proj{\psi}$ by Thm.~\ref{thm:Finite-precision-Born}.
Since the maximum length of the intervals in $\mathscr{I}_{n}$ is
$1/n$, the difference between the Born quantum probabilities~$\left|\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right|$
is bounded by $1/n$.  This implies $\left\Vert \rho-\rho'\right\Vert \le\frac{1}{n}$
by definition.

>>>>

In other words, if the measurement intervals are too imprecise, the
results we get might contradict to each other, and exclude any possible
state being consistent with the measurement results. Although we will
not dig into the general framework to avoid this problem here~\citep{HOSTunpublished},
we will address this problem with a concrete family of intervals and
QIVPMs. Consider the following intervals 
\begin{equation}
\begin{aligned}\mathscr{I}_{n}= & \set{\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]\cap\left[0,1\right]}{k=0,\ldots,2n}\\
 & \cup\{\imposs,\necess\}
\end{aligned}
\end{equation}
which are overlapping intervals with length~$1/n$ except for the
intervals with length~$\left(2n\right)^{-1}$ at each end. As shown
in Table~\ref{tab:I_n}, for each interval~$[\ell,r]$, we define
$\textrm{Int}\left([\ell,r]\right)$, the non-overlapping interior
part of $[\ell,r]$.
\begin{table}
\caption{\label{tab:I_n}Intervals in $\mathscr{I}_{n}$, their lengths, and
their interiors, where $2\mid k$ means $k$ is even, and $2\nmid k$
means $k$ is odd. Although intervals~$[\ell,r]$ are overlapping,
their interior~$\textrm{Int}\left([\ell,r]\right)$ are non-overlapping.}

\begin{tabular}{cccc}
\toprule 
\addlinespace
$k$ & $[\ell,r]$ & $r-\ell$ & $\textrm{Int}\left([\ell,r]\right)$\tabularnewline\addlinespace
\midrule
\midrule 
\addlinespace
 & $\imposs$ & $0$ & $\imposs$\tabularnewline\addlinespace
\midrule 
\addlinespace
$0$ & $\left[0,\tfrac{1}{2n}\right]$ & $\tfrac{1}{2n}$ & $\left(0,\tfrac{0.5}{2n}\right]$\tabularnewline\addlinespace
\midrule 
\addlinespace
\begin{tabular}{c}
$0<k<2n$\tabularnewline
and $2\nmid k$\tabularnewline
\end{tabular} & $\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]$ & $\tfrac{1}{n}$ & $\left(\tfrac{k-0.5}{2n},\tfrac{k+0.5}{2n}\right)$\tabularnewline\addlinespace
\midrule 
\addlinespace
\begin{tabular}{c}
$0<k<2n$\tabularnewline
and $2\mid k$\tabularnewline
\end{tabular} & \multirow{1}{*}{$\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]$} & $\tfrac{1}{n}$ & $\left[\tfrac{k-0.5}{2n},\tfrac{k+0.5}{2n}\right]$\tabularnewline\addlinespace
\midrule 
\addlinespace
$2n$ & $\left[\tfrac{2n-1}{2n},1\right]$ & $\tfrac{1}{2n}$ & $\left[\tfrac{2n-0.5}{2n},1\right)$\tabularnewline\addlinespace
\midrule 
\addlinespace
 & $\necess$ & $0$ & $\necess$\tabularnewline\addlinespace
\bottomrule
\end{tabular}
\end{table}
Since their interior parts are non-overlapping, we can define a function~$\iota_{n}:\left[0,1\right]\rightarrow\mathscr{I}_{n}$
by $\iota_{n}\left(x\right)=[\ell,r]$ if $x\in\textrm{Int}\left([\ell,r]\right)$
to map a real-valued probability to an interval-valued one. This function
can then induce a QIVPM from a state according to the following theorem:

@@

In contrast with the QIVPM defined in Table~\ref{tab:non-Born-QIVPM},
there is always a state consistent with a Born QIVPM~$\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$
because $\rho\in\coreBorn\left(\left[\mu_{\rho}^{\mathrm{B}}\right]_{n},\events\right)$.
Moreover, with respect to a notion of distance between two states~$\rho$
and $\rho'$, $\left\Vert \rho-\rho'\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho-\rho'}{\psi}\right|$~\citep{544199},
the collection of states consistent with $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$
gets closer and closer to $\rho$ as the intervals get narrower and
narrower.

@@

\noindent Given a state~$\rho'$ consistent with $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$,
we have $\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)\in\iota_{n}\left(\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right)$
for any 1-dimensioal projector~$\proj{\psi}$. Since the maximum
length of the intervals in $\mathscr{I}_{n}$ is $1/n$, $1/n$ is
the upper bound of the difference between the Born quantum probabilities
$\left|\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right|=\left|\melem{\psi}{\rho-\rho'}{\psi}\right|$.
 This implies $\left\Vert \rho-\rho'\right\Vert \le\frac{1}{n}$ by
definition.
